Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-24 paper/paper.tex

\section*{Introduction}
The similarity of two items is a valuable measurement for a number of
data-mining applications, such as recommender systems. With large amounts of
rating data, collaborative filtering is a good method for calculating
similarity. However, with sparse rating data, this technique gives noisy and
unreliable approximations for similarity. Even worse, low confidence
measurements of similarity are indistinguishable from high confidence ones. In
this paper, we develop a novel method which incorporates confidence into the
similarity score to produce more accurate estimates of similarity.

>>>>

\section*{Introduction}
The similarity of two items is a valuable measurement for a number of
data-mining applications, such as recommender systems. With large amounts of
rating data, collaborative filtering is a good method for calculating
similarity. However, with sparse rating data, this technique gives noisy and
unreliable approximations for similarity. Even worse, low confidence
measurements of similarity are indistinguishable from high confidence ones. In
this paper, we develop and compare a number of methods to produce more accurate
estimates of similarity by incorporating confidence into the similarity score.
